Co-citations in context

### 2019-07-19 rebuttal.tex

\newpage

\emph{Figure 2 is informative, it shows that when using local network instead of global network, the Uzzi finding still holds for the whole WoS database but not for applied physics, immunology, or metabolism. However, there are two possible explanations: (1) Uzzi's findings are not universal across fields, and (2) difference in using local vs. global networks.  It would be helpful to replicate the same plots using Uzzi's global network approach and single out which factor made the difference.}

Please see the figure included in this response (noted as Figure 1), which was not included in the submitted paper due to space limitations. The figure specifically addresses the reviewer's point, and shows that both factors are in play:  (i) there is a difference when local and global networks are used to generate expected values, and  (ii)  disciplines can be different from each other. While we do not think this figure needs to be included in the manuscript, we  could include if necessary or make it available as supplementary material through FigShare or some other site.

### 2019-07-28 rebuttal.tex

\emph{On page 2, `In addition, under this random model, a reference cited many times in a given year is selected with the same probability as a reference cited only once, which appears inconsistent with the power law or lognormal citation distributions described in the literature.'  I do not quite understand this.  In Uzzi's reference swapping, for each references, its total number of forward citations is preserved, so at the system level, a reference with fewer citations does have a smaller probability of being swapped.  So I do not exactly understand this criticism.}

Our apologies for not being clear. In the  revised manuscript, we have also highlighted a section of the Materials and Methods that is relevant. In examining the citation shuffling code of Uzzi kindly shared by Satyam Mukherjee and Ben Jones, we realized that the choice of substitutions was restricted to the set rather than the multi-set of eligible references. While their reciprocal substitution approach  ensures that the total number of references stratified by year of publication is still preserved after shuffling, the selection of a substituent is equiprobable. In either a local or a global network, it does not make sense to treat a highly cited reference as equiprobable with a reference cited only once. This flies in the face of what we know about preferential attachment and citation practice.

Consider a toy Web of Science dataset consisting of 5 publications all published in the same year. Each of these publications cites 4 references, thus, 20 citations. For simplicity, we will assume that all of these references were published in the same year. Of these, one (which we will call $x$) is cited in each of the publications (thus cited 5 times) and the remaining 15 are cited once in total. During citation shuffling (i)  in our approach, the probability of selecting $x$ would be 5/20 or 1/4. In Uzzi it would be 1/16. The remaining 15 references in Uzzi would have a probability of 1/16, whereas in our model they would have a probability of 1/20. In other words, Uzzi's algorithm seeks to systematically shuffle every reference in the network but replacements are selected from the set \{x,a,b,c,d,e...n\} rather than the multi-set \{x,x,x,x,x,a,b,c,d,e...n\} of eligible references.

### 2019-09-10 cocit_r_v2.tex
added Wang, Veugelers, and Stephan reference and early edits

\textcolor{blue}{Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions. The citation switching algorithm used to generate expected values by substituting cited references with randomly selected references published in the same year is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references. Importantly, disciplinary origin does not affect the probability that a reference is selected to replace another one. For example, a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology. Such substitutions poorly model the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}. In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once, which is inconsistent with the power law or lognormal citation distributions of citations described in the literature~\citep{stringer_statistical_2010,perline_strong_2005}.  Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.}

>>>>

\textcolor{green}{A related study by \cite{wang_bias_2017} does...fill in the blanks}

\textcolor{blue}{Key to the findings of Uzzi {\em et al.}~is the random graph model used, and its underlying assumptions. The citation switching algorithm used to generate expected values by substituting cited references with randomly selected references published in the same year is designed to preserve the number of publications, the number of references in each publication, and the year of publication of both publications and references. Importantly, disciplinary origin does not affect the probability that a reference is selected to replace another one. For example, a reference in quantum physics can be substituted, with equal probability, by a reference in quantum physics, quantum chemistry, classical literature, entomology, or anthropology. Such substitutions poorly model the disciplinary nature of scientific research and citation behavior~\citep{wallace_lariviere_gingras_2012,moed_measuring_2010,klavans_research_2017,garfield_1979}. \textcolor{green}{In addition, under this random model, a reference cited many times in a given year is selected as a substituent with the same probability as a reference cited only once}. Accordingly, model misspecification is likely to arise on account of the simulated values not corresponding to the empirical data very well.}
